---
title: "Supplementary Materials for XX title"
author: "Goumi A, Wlodarczyk V, Gosling CJ & Pinabiaux C"
output:
  html_document:
    toc: yes
    toc_float: yes
    self_contained: yes
---

---

```{css, echo=FALSE}
hr {
  margin-top: 5rem !important;
  margin-bottom: 5rem !important;
  border-top: 3px double !important;
}
```

```{r, message=FALSE, warning=FALSE, echo = FALSE, results = 'hide'}
library(ggplot2)
library(dplyr)
library(tidyr)
library(TOSTER)
library(table1)
library(emmeans)
library(metaviz)
smd <- function(x, df, level) {
    df_smd = data.frame(x)
    n2 = nrow(df[which(df[, "group"] == "Control"), ])
    n1 = nrow(df[which(df[, "group"] == "Experimental"), ])
    sd_n2 = sd(df[which(df[, "group"] == "Control"), ]$z1)
    sd_n1 = sd(df[which(df[, "group"] == "Experimental"), ]$z1)
    res = compute.es::mes(m.1 = df_smd$emmean[2], m.2 = df_smd$emmean[1], 
                          sd.1 = sd_n1, sd.2 = sd_n2, 
                          n.1 = n1, n.2 = n2,
                          df_smd$emmean[2],
                          verbose = FALSE,
                          level = level)
    return(list(res$d, res$l.d, res$u.d, paste0("SMD = ", res$d, " [", res$l.d, ", ", res$u.d, "]")))
}

```

```{r, message=FALSE, warning=FALSE, echo = FALSE, results = 'hide'}
dat_long = read.delim("data_beebot.txt")

dat_long$value = with(dat_long, ifelse(flip == "yes", -value, value))
```

```{r, message=FALSE, warning=FALSE, echo = FALSE, results = 'hide'}
# we translate the data + center our outcomes at t0 and t1 + assess the pre/post correlation for each of our outcomes
dat_semiwide_raw <- 
  dat_long %>% 
  pivot_wider(names_from = "time", values_from = "value") %>%
  dplyr::group_by(outcome) %>%
  dplyr::mutate(z0 = as.numeric(as.character(scale(t0))),
                z1 = as.numeric(as.character(scale(t1))),
                r = as.numeric(as.character(cor.test(~t0 + t1)$estimate))) %>% 
  dplyr::ungroup()

dat_semiwide <- dat_semiwide_raw

```

```{r, message=FALSE, warning=FALSE, echo = FALSE}
dat_comp <- dat_semiwide %>%
  group_by(participant, experimentatrice, eleve, group, ID, age, sexe, GEN_outcome, flip) %>%
  summarise(z0 = sum(z0),
            z1 = sum(z1))
```

```{r, message=FALSE, warning=FALSE, echo = FALSE, results = 'hide'}
dat_wide1 <- dat_comp %>%
  dplyr::select(-c(z1, flip)) %>%
  pivot_wider(names_from = GEN_outcome, values_from = z0)

dat_wide2 <- dat_long %>%
  filter(time == "t0") %>%
  dplyr::select(-c(flip, GEN_outcome)) %>%
  pivot_wider(names_from = outcome, values_from = value)

dat_wide = dat_long %>%
  group_by(participant) %>%
  slice(1)


```

## I. Table1 
Demographic characteristics of our sample depending on the group.
```{r}
dat_wide$age <- as.numeric(as.character(dat_wide$age))
dat_wide$sex <- factor(dat_wide$sexe)

table1::table1(~ age + sex | group, data=dat_wide, overall = "Overall",
              render.continuous=c(.="Mean / Median<br>SD<br>[min, max]"))
```

Effect sizes of the group differences
```{r}
smd_age <- with(dat_wide, lsr::cohensD(age ~ group))
smd_age

chi <- with(dat_wide, chisq.test(table(sexe, group)))
confintr::cramersv(chi)
```

---

## II. Distributions{.tabset}

Outcome distribution at baseline

### Inhibition
```{r}
dat_inhib_dist <- subset(dat_long, grepl("Inhibition", dat_long$GEN_outcome) & time != "t1")

ggplot(dat_inhib_dist, aes(x = value)) + 
  geom_histogram(aes(y=..density..), fill = "grey", alpha = 0.8) + 
  geom_density(alpha = 0.3, aes(fill = group)) + 
  facet_wrap(. ~ outcome, scales = "free") +
  theme_bw() + 
  theme(legend.position = "bottom")
  
```

---

### Working Memory
```{r}
dat_memory_dist <- subset(dat_long, grepl("memory", dat_long$GEN_outcome) & time != "t1")

ggplot(dat_memory_dist, aes(x = value)) + 
  geom_histogram(aes(y=..density..), fill = "grey", alpha = 0.8) + 
  geom_density(alpha = 0.3, aes(fill = group)) + 
  facet_wrap(. ~ outcome, scales = "free") +
  theme_bw() + 
  theme(legend.position = "bottom")
```

---

### Overal EF
```{r}
dat_EF_dist <- subset(dat_long, grepl("Executive", dat_long$GEN_outcome) & time != "t1")

ggplot(dat_EF_dist, aes(x = value)) + 
  geom_histogram(aes(y=..density..), fill = "grey", alpha = 0.8) + 
  geom_density(alpha = 0.3, aes(fill = group)) + 
  facet_wrap(. ~ GEN_outcome, scales = "free") +
  theme_bw() + 
  theme(legend.position = "bottom")
```

---

### Other
```{r}
dat_othr_dist <- subset(dat_long, !grepl("memory", dat_long$GEN_outcome) & !grepl("Inhibition", dat_long$GEN_outcome) & !grepl("Executive", dat_long$GEN_outcome) & time != "t1")

ggplot(dat_othr_dist, aes(x = value)) + 
  geom_histogram(aes(y=..density..), fill = "grey", alpha = 0.8) + 
  geom_density(alpha = 0.3, aes(fill = group)) + 
  facet_wrap(. ~ outcome, scales = "free") +
  theme_bw() + 
  theme(legend.position = "bottom")

```

---

## III. Preliminary analyses

### BeeBot mastering
```{r}
dat_eval = subset(dat_wide, s4_bin == 1)
paste0(round(nrow(dat_eval)/sum(!is.na(dat_wide$s4_bin))*100, 3), "% of the sample succeed at a beebot mastering test after the last training session, with a mean score of ", round(mean(dat_eval$s4_0_4), 3), "/4")

```

### Correlation between tests
```{r, fig.width = 15, fig.height=10}
ggstatsplot::ggcorrmat(dat_wide1[,which(colnames(dat_wide1) == "Denomination (NEPSY-II)"):ncol(dat_wide1)],
          p.adjust.method = "none",
          ggtheme = ggplot2::theme_bw(),
          colors = c("#0016FF", "white", "#FF0000"),
          sig.level = 0.99)
```

```{r, fig.width = 15, fig.height=10}
# ggstatsplot::ggcorrmat(dat_wide2[,which(colnames(dat_wide2) == "Planification (KABC-II)"):ncol(dat_wide2)],
#           p.adjust.method = "none",
#           ggtheme = ggplot2::theme_bw(),
#           colors = c("#0016FF", "white", "#FF0000"),
#           sig.level = 0.05)
```

---

## IV. Main analysis 

```{r, message=FALSE, warning=FALSE, echo = FALSE}
no = length(unique(dat_comp$GEN_outcome))
res_main <- data.frame(outcome = rep(NA, no),
                       flip = rep(NA, no),
                       n_cont  = rep(NA, no),
                       n_exp = rep(NA, no),
                       d = rep(NA, no) ,
                       d_se = rep(NA, no) ,
                       d_low = rep(NA, no),
                       d_up = rep(NA, no),
                       d_tot = rep(NA, no),
                       B = rep(NA, no),
                       SE = rep(NA, no),
                       p = rep(NA, no))
a = 0

for (out in unique(dat_comp$GEN_outcome)) {
  # initialize some settings and re-initializing them as NA at each loop
  a = a+1
  mod = d = means = NA
  
  # subset dataframe ----------------
  dat_i = subset(dat_comp, GEN_outcome == out)
  
  ## ancova pre/post adjusted
  mod = lm(z1 ~ group + z0 + age + sexe, data = dat_i)
  means = emmeans::emmeans(mod, ~factor(group))
  # identify critical information ------------------------------------------------------------
  res_main$outcome[a] = out
  res_main$flip[a] = unique(dat_i$flip)
  res_main$n_cont[a] = nrow(subset(dat_i, group == "Control"))
  res_main$n_exp[a] = nrow(subset(dat_i, group == "Experimental"))
  res_main$B[a] = summary(mod)$coefficients[2,1]
  res_main$SE[a] = summary(mod)$coefficients[2,2]
  res_main$p[a] = summary(mod)$coefficients[2,4]

  # extract results ---------
  d = smd(x = means, df = dat_i, level = 95)
  
  res_main$d[a] = d[[1]]
  res_main$d_low[a] = d[[2]]
  res_main$d_up[a] = d[[3]]
  res_main$d_tot[a] = d[[4]]
}
res_main$d_se = (res_main$d_up - res_main$d_low) / (2*1.96)
### TOST analysis
res_main$TOST <- NA
for (i in 1:nrow(res_main)) {
  res_main$TOST[i] <- max(
    abs(tsum_TOST(m1 = res_main$d[i], m2 = 0, sd1 = 1, sd2 = 1, 
              n1 = res_main$n_cont[i], n2 = res_main$n_exp[i], 
              low_eqbound = -0.8, high_eqbound = 0.8, alpha = 0.05,
              var.equal = FALSE, bias_correction = FALSE,
              eqbound_type = "raw")$smd$dhigh),
    abs(tsum_TOST(m1 = res_main$d[i], m2 = 0, sd1 = 1, sd2 = 1, 
              n1 = res_main$n_cont[i], n2 = res_main$n_exp[i], 
              low_eqbound = -0.8, high_eqbound = 0.8, alpha = 0.05,
              var.equal = FALSE, bias_correction = FALSE,
              eqbound_type = "raw")$smd$dlow))
}

```

### Table
```{r}
res_main = res_main %>% mutate(across(where(is.numeric), round, digits=3))
DT::datatable(res_main, 
              rownames = FALSE,
              extensions = "Buttons",
              options = list(  # options
                scrollX = TRUE,
                dom = c('tB'), 
                buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                scrollY = "600px", 
                pageLength = 30,
                order = list(4, 'asc'),
                columnDefs = list(
                  list(width = '70px',
                       targets = "_all"),
                  list(className = 'dt-center', 
                       targets = "_all"))))
```

---

### Forest plot
```{r, warning = FALSE}
tab.main <- data.frame(
  'General outcome' = res_main$outcome,
  TOST = res_main$TOST)

metaviz::viz_forest(x = res_main[, c("d", "d_se")], 
           variant = "classic",
           col = "Greys", xlab = "SMD", annotate_CI = TRUE, 
           study_table = tab.main,
           type = "study_only",
           text_size = 2.5,
           x_limit = c(-1.5, 1.5),
           x_breaks = seq(-3, 3, 1))
```

---

### Box plots{.tabset}
```{r, echo = FALSE}
dat_plot <- 
  dat_comp %>%
  pivot_longer(
   cols = c(z0, z1),
   names_to = "time",
   values_to = "value",
  )
dat_plot$time[dat_plot$time == "z0"] <- "t0"
dat_plot$time[dat_plot$time == "z1"] <- "t1"
```

---

#### Inhibition
```{r}
dat_inhib <- subset(dat_plot, grepl("Inhibition", dat_plot$GEN_outcome))

ggplot(dat_inhib, aes(x = time, y = value, color = group, fill = group)) +
  # geom_line() +
  geom_boxplot(alpha = 0.2) +
  facet_grid(. ~ GEN_outcome,  scales = 'free') + 
theme_bw() + 
  theme(legend.position="bottom")
```

---

#### Working memory
```{r}
dat_memory <- subset(dat_plot, grepl("memory", dat_plot$GEN_outcome))

ggplot(dat_memory, aes(x = time, y = value, color = group, fill = group)) +
  geom_boxplot(alpha = 0.2) +
  facet_grid(. ~ GEN_outcome,  scales = 'free') + 
theme_bw()  + 
  theme(legend.position="bottom")
```

---

#### Overall EF
```{r}
dat_EF <- subset(dat_plot, grepl("Executive", dat_plot$GEN_outcome))

ggplot(dat_EF, aes(x = time, y = value, color = group, fill = group)) +
  geom_boxplot(alpha = 0.2) +
  facet_grid(. ~ GEN_outcome,  scales = 'free') + 
theme_bw()  + 
  theme(legend.position="bottom")
```

---

#### Others
```{r}
dat_othr <- subset(dat_plot, !grepl("memory", dat_plot$GEN_outcome) & !grepl("Inhibition", dat_plot$GEN_outcome) & !grepl("Executive", dat_plot$GEN_outcome))

ggplot(dat_othr, aes(x = time, y = value, color = group, fill = group)) +
  geom_boxplot(alpha = 0.2) +
  facet_grid(. ~ GEN_outcome,  scales = 'free') + 
  theme_bw() + 
  theme(legend.position="bottom")
```

---

## V. Additional analyses

### 1. No demographic covariates

```{r, echo = FALSE}
no = length(unique(dat_comp$GEN_outcome))
res_S2 <- data.frame(outcome = rep(NA, no),
                       flip = rep(NA, no),
                       n_cont  = rep(NA, no),
                       n_exp = rep(NA, no),
                       d = rep(NA, no) ,
                       d_se = rep(NA, no) ,
                       d_low = rep(NA, no),
                       d_up = rep(NA, no),
                       d_tot = rep(NA, no),
                       B = rep(NA, no),
                       SE = rep(NA, no),
                       p = rep(NA, no))
a = 0

for (out in unique(dat_comp$GEN_outcome)) {
  # initialize some settings and re-initializing them as NA at each loop
  a = a+1
  mod = d = means = NA
  
  # subset dataframe ----------------
  dat_i = subset(dat_comp, GEN_outcome == out)
  
  ## ancova pre/post adjusted
  mod = lm(z1 ~ group + z0, data = dat_i)
  means = emmeans::emmeans(mod, ~factor(group))
  # identify critical information ------------------------------------------------------------
  res_S2$outcome[a] = out
  res_S2$flip[a] = unique(dat_i$flip)
  res_S2$n_cont[a] = nrow(subset(dat_i, group == "Control"))
  res_S2$n_exp[a] = nrow(subset(dat_i, group == "Experimental"))
  res_S2$B[a] = summary(mod)$coefficients[2,1]
  res_S2$SE[a] = summary(mod)$coefficients[2,2]
  res_S2$p[a] = summary(mod)$coefficients[2,4]

  # extract results ---------
  d = smd(x = means, df = dat_i, level = 95)
  
  res_S2$d[a] = d[[1]]
  res_S2$d_low[a] = d[[2]]
  res_S2$d_up[a] = d[[3]]
  res_S2$d_tot[a] = d[[4]]
}
res_S2$d_se = (res_S2$d_up - res_S2$d_low) / (2*1.96)
### TOST analysis
res_S2$TOST <- NA
for (i in 1:nrow(res_S2)) {
  res_S2$TOST[i] <- max(
    abs(tsum_TOST(m1 = res_S2$d[i], m2 = 0, sd1 = 1, sd2 = 1, 
              n1 = res_S2$n_cont[i], n2 = res_S2$n_exp[i], 
              low_eqbound = -0.8, high_eqbound = 0.8, alpha = 0.05,
              var.equal = FALSE, bias_correction = FALSE,
              eqbound_type = "raw")$smd$dhigh),
    abs(tsum_TOST(m1 = res_S2$d[i], m2 = 0, sd1 = 1, sd2 = 1, 
              n1 = res_S2$n_cont[i], n2 = res_S2$n_exp[i], 
              low_eqbound = -0.8, high_eqbound = 0.8, alpha = 0.05,
              var.equal = FALSE, bias_correction = FALSE,
              eqbound_type = "raw")$smd$dlow))
}

```

#### Table
```{r}
res_S2 = res_S2 %>% mutate(across(where(is.numeric), round, digits=3))
DT::datatable(res_S2, 
              rownames = FALSE,
              extensions = "Buttons",
              options = list(  # options
                scrollX = TRUE,
                dom = c('tB'), 
                buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                scrollY = "600px", 
                pageLength = 30,
                order = list(4, 'asc'),
                columnDefs = list(
                  list(width = '70px',
                       targets = "_all"),
                  list(className = 'dt-center', 
                       targets = "_all"))))
```

#### Forest plot
```{r, warning = FALSE}
tab.S2 <- data.frame(
  'General outcome' = res_S2$outcome,
  TOST = res_S2$TOST)

metaviz::viz_forest(x = res_S2[, c("d", "d_se")], 
           variant = "classic",
           col = "Greys", xlab = "SMD", annotate_CI = TRUE, 
           study_table = tab.S2,
           type = "study_only",
           text_size = 2.5,
           x_limit = c(-1.5, 1.5),
           x_breaks = seq(-3, 3, 1))
```

---

### 2. All outcomes

```{r, echo = FALSE}
row = length(unique(dat_semiwide$outcome))
res_S1 <- data.frame(outcome = rep(NA, row),
                       flip = rep(NA, row),
                       n_cont  = rep(NA, row),
                       n_exp = rep(NA, row),
                       d = rep(NA, row) ,
                       d_se = rep(NA, row) ,
                       d_low = rep(NA, row),
                       d_up = rep(NA, row),
                       d_tot = rep(NA,row),
                       B = rep(NA, row),
                       SE = rep(NA, row),
                       p = rep(NA, row))
a = 0

for (out in unique(dat_semiwide$outcome)) {
  # initialize some settings and re-initializing them as NA at each loop
  a = a+1
  mod = d = means = NA
  
  # subset dataframe ----------------
  dat_i = subset(dat_semiwide, outcome == out)
  
  ## ancova pre/post adjusted
  mod = lm(z1 ~ group + z0 + age + sexe, data = dat_i)
  means = emmeans::emmeans(mod, ~factor(group))
  # identify critical information ------------------------------------------------------------
  res_S1$outcome[a] = out
  res_S1$flip[a] = unique(dat_i$flip)
  res_S1$n_cont[a] = nrow(subset(dat_i, group == "Control"))
  res_S1$n_exp[a] = nrow(subset(dat_i, group == "Experimental"))
  res_S1$B[a] = summary(mod)$coefficients[2,1]
  res_S1$SE[a] = summary(mod)$coefficients[2,2]
  res_S1$p[a] = summary(mod)$coefficients[2,4]

  # extract results ---------
  d = smd(x = means, df = dat_i, level = 95)
  
  res_S1$d[a] = d[[1]]
  res_S1$d_low[a] = d[[2]]
  res_S1$d_up[a] = d[[3]]
  res_S1$d_tot[a] = d[[4]]
}
res_S1$d_se = (res_S1$d_up - res_S1$d_low) / (2*1.96)
### TOST analysis
res_S1$TOST <- NA
for (i in 1:nrow(res_S1)) {
  res_S1$TOST[i] <- max(
    abs(tsum_TOST(m1 = res_S1$d[i], m2 = 0, sd1 = 1, sd2 = 1, 
              n1 = res_S1$n_cont[i], n2 = res_S1$n_exp[i], 
              low_eqbound = -0.8, high_eqbound = 0.8, alpha = 0.05,
              var.equal = FALSE, bias_correction = FALSE,
              eqbound_type = "raw")$smd$dhigh),
    abs(tsum_TOST(m1 = res_S1$d[i], m2 = 0, sd1 = 1, sd2 = 1, 
              n1 = res_S1$n_cont[i], n2 = res_S1$n_exp[i], 
              low_eqbound = -0.8, high_eqbound = 0.8, alpha = 0.05,
              var.equal = FALSE, bias_correction = FALSE,
              eqbound_type = "raw")$smd$dlow))
}
```

#### Table
```{r}

res_S1 = res_S1 %>% mutate(across(where(is.numeric), round, digits=3))

DT::datatable(res_S1, 
              rownames = FALSE,
              extensions = "Buttons",
              options = list(  # options
                scrollX = TRUE,
                dom = c('tB'), 
                buttons = c('copy', 'csv', 'excel', 'pdf', 'print'),
                scrollY = "600px", 
                pageLength = 30,
                order = list(4, 'asc'),
                autoWidth = TRUE,
                columnDefs = list(
                  list(width = '70px',
                       targets = "_all"),
                  list(className = 'dt-center', 
                       targets = "_all"))))
```

#### Forest plot
```{r, warning = FALSE}

tab.supp <- data.frame(
  Outcome = res_S1$outcome,
  TOST = res_S1$TOST)

metaviz::viz_forest(x = res_S1[, c("d", "d_se")], 
           variant = "classic",
           col = "Greys", xlab = "SMD", annotate_CI = TRUE, 
           study_table = tab.supp,
           type = "study_only",
           text_size = 2.2,
           x_limit = c(-1.5, 1.5),
           # N = tab.prim$N,
           x_breaks = seq(-3, 3, 1))
```

---

### 3. Beebot mastering

```{r}
dat_semiwide$z_change = dat_semiwide$z1 - dat_semiwide$z0
dat_s3 = subset(dat_semiwide, !is.na(s4_0_4))
dat_s3$s4_bin = factor(dat_s3$s4_bin)

summary(lmerTest::lmer(z_change ~ ordered(s4_0_4) + (1|participant) + (1|outcome), data = dat_s3))

res_s3_bin = lmerTest::lmer(z_change ~ s4_bin + (1|participant) + (1|outcome), data = dat_s3)
summary(res_s3_bin)
emmeans(res_s3_bin, ~s4_bin)

ggplot(dat_s3, aes(x = s4_0_4, y = z_change)) + 
  geom_jitter(width=0.2, size = 2, alpha = 0.4) + 
  theme_bw()

ggplot(dat_s3, aes(x = factor(s4_bin), y = z_change)) + 
  geom_jitter(width=0.1, size = 2, alpha = 0.4) + 
  theme_bw()

```


```{r}
# dat_agg <-
#   dat_long %>%
#   # pivot_wider(names_from = "time", values_from = "value") %>%
#   dplyr::group_by(outcome) %>%
#   dplyr::mutate(z = scale(value)) %>%
#   dplyr::ungroup() %>%
#   dplyr::group_by(time, ID, group) %>%
#   summarise(value_z = sum(z))
# 
# ID <- 
#   dat_agg %>%
#   group_by(ID) %>%
#   arrange(time) %>%
#   mutate(diff = value_z - lag(value_z, default = first(value_z))) %>%
#   filter(time == "t1") %>%
#   mutate(Improvement = if_else(diff > 0, "Improvement", "Deterioration"))%>%
#   dplyr::select(ID, Improvement) %>%
#   filter(!is.na(Improvement))
#  
# dat_line <- merge(dat_agg, ID, by = "ID")
```

```{r}
# ggplot(dat_line, aes(x = time, y = value_z, color = group, group = ID)) +
#   geom_point(size = 2.5, alpha = 0.4) + 
#   geom_line(size = 1, linetype  = "dotted", alpha = 0.8) +
#   theme_bw() + 
#   facet_grid(group ~  Improvement) +
#   theme(legend.position = "none")
```


```{r, echo = FALSE, results = 'hide'}
# summary(lm(t1_corsi_end_nb ~ group + t0_corsi_end_nb + age + sexe, data = dat))
# summary(lm(t1_corsi_end_nb ~ group + t0_corsi_end_nb, data = dat))
# summary(lm(t1_corsi_end_nb ~ group, data = dat))
# dat$corsi = dat$t1_corsi_end_nb - dat$t0_corsi_end_nb
# summary(lm(corsi ~ group, data = dat))
```

